pirouette: Determining the error BEAST2 makes in inferring a phylogeny

### 2019-03-11 article.tex

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{figure_example_1.png}
  \caption{
    Example 1: the error BEAST2 makes from a phylogeny 
    when the generative and inference model are the same.
  }
  \label{fig:example_1}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{figure_example_2.png}
  \caption{
    Example 2: the error BEAST2 makes from a phylogeny when
    picking the best inference model.
    The x-axis specifies the tree type (which can be 'true' or 'twin'), 
    the y-axis shows the error
  }
  \label{fig:example_2}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{figure_example_3.png}
  \caption{
    Example 3: the error made by BEAST2 from a phylogeny, picking the best inference model versus the control.
    Here, the twin column shows the error BEAST2 makes starting from the original tree versus the twin. 
    The x-axis specifies the tree type (which can be 'true' or 'twin'), the y-axis shows the error.
    The boxplot shows the minimum, first quartile, median, third 
    quartile and maximum error, of which the values are displayed 
    in the adjacent label.
  }
  \label{fig:example_3}
  \giovanni{remove boxplots}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{figure_example_4.png}
  \caption{
    Example 4: the error made by BEAST2 from a phylogeny, when the generative model is known, compared to candidates with similar inference models, in relationship to the background error.
    The x-axis specifies the tree type, the y-axis shows the error.
    The boxplot shows the minimum, first quartile, median, third 
    quartile and maximum error, of which the values are displayed 
    in the adjacent label.
  }
  \label{fig:example_4}
  \giovanni{Remove boxplots.}
\end{figure}

@@

\begin{figure}[h]
  \includegraphics[width=\textwidth]{figure_example_5.png}
  \caption{
    Example 5: the error made by BEAST2 from a phylogeny, when the generative model is known, compared to candidates with similar inference models, in relationship to the background error.
    The x-axis specifies the tree type, the y-axis shows the error.
    The boxplot shows the minimum, first quartile, median, third 
    quartile and maximum error, of which the values are displayed 
    in the adjacent label
  }
  \label{fig:example_5}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.25\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1_true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1_true_alignment.png}
    };   
    \node[state] (C) [below of = B, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1_true_posterior_gen.png}
    };   
    \node[state] (D) [below of = C, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1_error_violin.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (C)
      (C) edge [anchor = south] node {} (D)
    ; 
    \end{tikzpicture}
  }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{example_1_errors.png}
  \caption{
    Example 1: the error BEAST2 makes from a phylogeny 
    when the generative and inference model are the same.
  }
  \label{fig:example_1}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{example_2_errors.png}
  \caption{
    Example 2: the error BEAST2 makes from a phylogeny when
    picking the best inference model.
  }
  \label{fig:example_2}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{example_3_errors.png}
  \caption{
    Example 3: the error made by BEAST2 from a phylogeny, picking the best inference model versus the control.
    Here, the twin column shows the error BEAST2 makes starting from the original tree versus the twin. 
  }
  \label{fig:example_3}
  \giovanni{remove boxplots}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{example_4_errors.png}
  \caption{
    Example 4: the error made by BEAST2 from a phylogeny, when the generative model is known, compared to candidates with similar inference models, in relationship to the background error.
  }
  \label{fig:example_4}
  \giovanni{Remove boxplots.}
\end{figure}

@@

\begin{figure}[h]
  \includegraphics[width=\textwidth]{example_5_errors.png}
  \caption{
    Example 5: the error made by BEAST2 from a phylogeny, when the generative model is known, compared to candidates with similar inference models, in relationship to the background error.
    The x-axis specifies the tree type, the y-axis shows the error.
    The boxplot shows the minimum, first quartile, median, third 
    quartile and maximum error, of which the values are displayed 
    in the adjacent label
  }
  \label{fig:example_5}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.25\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1_true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1_true_alignment.png}
    };   
    \node[state] (C) [below of = B, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1_true_posterior_gen.png}
    };   
    \node[state] (D) [below of = C, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1_error_violin.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (C)
      (C) edge [anchor = south] node {} (D)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_1_full_pipeline}
  \caption{Example 1: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.25\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.2\textheight]{example_2_true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.2\textheight]{example_2_true_alignment.png}
    };   
    \node[state] (C) [below of = B, rectangle] {
      \includegraphics[height=0.2\textheight]{example_2_true_posterior_gen.png}
    };   
    \node[state] (D) [below of = C, rectangle] {
      \includegraphics[height=0.2\textheight]{example_2_error_violin.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (C)
      (C) edge [anchor = south] node {} (D)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_2_full_pipeline}
  \caption{Example 2: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
